### 2020-05-11 README.Rmd
added license and info about our package logos

### Usage of AIMS Data Platform API Key

@@

### Possible .Renviron file locations

@@

### Installation

@@

### Available Data Sets

@@

### Further Information

@@

>>>>

## Usage of AIMS Data Platform API Key

@@

## Possible .Renviron file locations

@@

## Installation

@@

## Available Data Sets

@@

## Further Information

@@

## AIMS R package logos

Our R package logos use a watercolour map of Australia, obtained with the [ggmap](https://cran.r-project.org/web/packages/ggmap/) R package, which downloads original map tiles provided by [Stamen Design](http://stamen.com), under [CC BY 3.0](http://creativecommons.org/licenses/by/3.0), with data from [OpenStreetMap](http://openstreetmap.org), under [CC BY SA](http://creativecommons.org/licenses/by-sa/3.0).
